\documentclass[]{awesome-cv}
\usepackage{textcomp}
\fontdir[fonts/]
\newcommand*{\sectiondir}{resume/}
\colorlet{awesome}{awesome-red}

\begin{document}

\begin{center}
    \headerfirstnamestyle{Facundo} \headerlastnamestyle{Giacconi} \\
    \vspace{2mm}
    {\faEnvelope\ fgiacconi.dev@gmail.com} | {\faMobile\ (+34) 679122423} | {\faMapMarker\ Girona, Spain}
    {\faLinkedin\ \href{https://www.linkedin.com/in/facundo-giacconi-fernandez-a77989a3}{Facundo}}
\end{center}

\begin{cvparagraph}
\textendash{} Senior Full Stack Developer with over 10 years of experience in web and mobile application development. Expert in technologies such as Java, Spring Boot, Angular, and React. Skilled in Agile and Scrum methodologies, with experience in implementing CI/CD.
\end{cvparagraph}

\cvsection{Skills}
\begin{cventries}
    \cventry
    {}
    {\def\arraystretch{1.15}{\begin{tabular}{l l}
        Languages: & {\skill{Java, JavaScript, TypeScript, C\#, SQL, HTML, CSS, Ruby on Rails, JSP}} \\
        Frameworks: & {\skill{Spring, Spring Boot, AngularJs, Angular (6-13), React, Nextjs}} \\
        Databases: & {\skill{MySQL, PostgreSQL, Oracle, SQLite, MongoDb}} \\
        Technologies / Tools: & {\skill{Docker, Jenkins, RabbitMQ, Kafka, SonarQube, Maven, Gradle, REST, Java JPA, Hibernate, npm, Yarn, Git, Gitlab, Subversion}} \\
        Practices: & {\skill{Agile, Scrum, Test-Driven Development, CI/CD, Code Reviews}} \\
    \end{tabular}}}
    {}
    {}
    {}
\end{cventries}

\cvsection{Experience}
\begin{cventries}
    \cventry
    {Full Stack Developer \& R\&D}
    {Azimut Electronics}
    {Gandía, Spain}
    {2022/04 – Present}
    {\begin{cvitems}
        \item {Development and improvement of digital multimedia and entertainment programs for public transportation.}
        \item {Project with AngularJs frontend and Spring Boot backend, connectivity to MongoDB, and REST communications.}
        \item {Development of applications with NextJs, React, and NodeJs with sequelize and MySQL.}
        \item {Collaboration on support tool applications based on Python (flask, tkinter, pymongo).}
    \end{cvitems}}

    \cventry
    {Full Stack Developer}
    {Sopra Steria}
    {Madrid, Spain}
    {2021/08 – 2022/04}
    {\begin{cvitems}
        \item {Development and improvement of an insurance product management project with Angular 6 frontend and Spring Boot backend.}
        \item {Communication between microservices with Apache Kafka and Zookeeper.}
    \end{cvitems}}

    \cventry
    {Full Stack Developer}
    {DXC Technology}
    {Girona, Spain}
    {2016/11 – 2021/08}
    {\begin{cvitems}
        \item {Development on governmental projects using Angular, Spring Boot, and Elasticsearch.}
        \item {Facilitated the transition to Angular 6, training the team and ensuring a smooth migration.}
    \end{cvitems}}

    \cventry
    {Full Stack Developer}
    {Coditramuntana}
    {Girona, Spain}
    {2016/02 – 2016/11}
    {\begin{cvitems}
        \item {Development of CRM and SPA projects based on Ruby on Rails with MySQL.}
        \item {Development of scientific and data calculation projects in Ruby on Rails.}
    \end{cvitems}}

    \cventry
    {Full Stack Developer}
    {Terramar Tours}
    {Lloret De Mar, Spain}
    {2013/06 – 2016/02}
    {\begin{cvitems}
        \item {Development and maintenance of an automatic travel schedule management system with Java Spring and SQL.}
        \item {Development of travel scheduling search API with Spring and Java.}
        \item {Development of relationship API with Spring, Java, and JOOQ.}
    \end{cvitems}}
    \vspace{10mm}
\end{cventries}

\cvsection{Projects}
\begin{cventries}
    \cventry
    {}
    {Pizzapp}
    {Java 17, Spring Boot 3.2.0, Angular 17, NodeJs 5, Websockets, MongoDB, Redis, Docker}
    {}
    {\begin{cvitems}
        \item {Web application for pizza orders with Angular 17 frontend and microservices backend.
        \newline \faLink\ \href{https://github.com/flautarian/pizzapp}{Github repository}}
    \end{cvitems}}

    \cventry
    {}
    {Owncloud}
    {Java 17, Spring Boot, AngularJs 1.5, MongoDB, Gitlab}
    {}
    {\begin{cvitems}
        \item {Enterprise CRM for managing multimedia content in buses and long-distance transports.}
        \item {Real-time communication system with client terminals.}
        \item {Multimedia content management system.}
        \item {Integration system with multimedia content DRM.
        \newline \faLink\ \href{https://www.azimutelectronics.com}{Corporate homepage}}
    \end{cvitems}}

    \cventry
    {}
    {Allianz Simulation Tool}
    {Java 11, Spring Boot, Apache Kafka, Angular 13, Subversion}
    {}
    {\begin{cvitems}
        \item {Tool for creating and calculating provisional policies for Allianz.}
        \item {Wizard-type form advancement system, with separate and isolated form phases.
        \newline \faLink\ \href{https://www.allianzdirect.es/seguro-de-coche/calcular-precio/}{Policy simulator}}
    \end{cvitems}}

    \cventry
    {}
    {Public Contracting Services Platform}
    {Java 8, Spring Boot, Elasticsearch, Angular, Github, PostgreSQL}
    {}
    {\begin{cvitems}
        \item {Development of a new platform in Angular starting from Adobe Flash Player.}
        \item {Tendering system with different contract phases.}
        \item {Development of communication system between bidders and clients.}
        \item {Development of digital envelope management system.}
        \item {Development of digital signature system for awards.
        \newline \faLink\ \href{https://contractaciopublica.cat/ca/inici}{Public contracting services platform}}
    \end{cvitems}}

    \cventry
    {}
    {Multi-purpose API based on Python}
    {Python 3, Mongodb 6, Flask, Github}
    {}
    {\begin{cvitems}
        \item {Private backend API for personal applications with Python, Flask, and MongoDB.}
    \end{cvitems}}

    \cventry
    {}
    {SocketIO Communication System based on Python}
    {Python 3, Flask, Github}
    {}
    {\begin{cvitems}
        \item {Private backend API for socket IO communication with Python, Flask, and MongoDB.}
    \end{cvitems}}

    \cventry
    {}
    {SocketIO Message Communication API based on Python}
    {Python 3, Mongodb 6, Flask, Github}
    {}
    {\begin{cvitems}
        \item {Private backend API for personal applications with Azure Functions and MongoDB.}
    \end{cvitems}}

    \cventry
    {}
    {TrelloApp}
    {React 18, Typescript, Sonner, Beaufitul-DnD, Github, Vercel, react18Next}
    {}
    {\begin{cvitems}
        \item {Trello-like application to reinforce knowledge of React.
        \newline \faLink\ \href{https://trello-app-giacconidev.vercel.app/user/login}{TrelloApp}}
    \end{cvitems}}
    \vspace{25mm}
\end{cventries}

\cvsection{Education}
\begin{cventries}
    \cventry
    {}
    {Instituto Montilivi}
    {Girona, Spain}
    {}
    {\begin{cvitems}
        \item {Higher education in System Network Administration (HNC)}
    \end{cvitems}}

    \cventry
    {}
    {Universitat Oberta de Catalunya}
    {Girona, Spain}
    {}
    {\begin{cvitems}
        \item {Bachelor's degree in Computer Engineering}
    \end{cvitems}}
\end{cventries}

\cvsection{Courses}
\begin{cventries}
    \cventry
    {}
    {A hundred Python projects}
    {Online}
    {}
    {\begin{cvitems}
        \item {70-hour course on Python, from native applications to webapps with Flask.
        \newline \faLink\ \href{https://www.udemy.com/certificate/UC-2d01021e-af92-434c-a4a3-7fc7b33976c9/}{Certificate of completion}}
    \end{cvitems}}

    \cventry
    {}
    {NextJs Course}
    {Online}
    {}
    {\begin{cvitems}
        \item {40-hour course on stateless web development with React and NextJs.
        \newline \faLink\ \href{https://www.udemy.com/certificate/UC-1ede8757-aa0d-406f-813a-8eaa400532c5/}{Certificate of completion}}
    \end{cvitems}}

    \cventry
    {}
    {React Course: From Basics to Advanced Applications}
    {Online}
    {}
    {\begin{cvitems}
        \item {50-hour course on React, from basics to advanced applications (Hooks, MERN).
        \newline \faLink\ \href{https://www.udemy.com/certificate/UC-fcb467ab-c089-419c-9b6a-afe97f894d14/}{Certificate of completion}}
    \end{cvitems}}

    \cventry
    {}
    {Spring University - Spring Framework and Spring Boot}
    {Online}
    {}
    {\begin{cvitems}
        \item {70-hour course on Spring Boot.
        \newline \faLink\ \href{https://www.udemy.com/certificate/UC-ee0ce349-6915-479b-b038-5253aba9d0d8/}{Certificate of completion}}
    \end{cvitems}}

    \cventry
    {}
    {Complete Guide to MongoDb Development 2022}
    {Online}
    {}
    {\begin{cvitems}
        \item {Course on Js, Jquery, Angular 9, and NodeJs with examples and best practices.
        \newline \faLink\ \href{https://www.udemy.com/certificate/UC-b990e98a-9b76-44b1-8e3e-43b68213725c/}{Certificate of completion}}
    \end{cvitems}}

    \cventry
    {}
    {Java Design Patterns Refresher Course}
    {Online}
    {}
    {\begin{cvitems}
        \item {Course on design patterns in Java with practical examples.
        \newline \faLink\ \href{https://www.udemy.com/certificate/UC-982e3338-ea7d-4434-bf27-af8e38b77bd5/}{Certificate of completion}}
    \end{cvitems}}
\end{cventries}

\cvsection{Additional Information}
\begin{cventries}
    \cventry
    {}
    {}
    {}
    {}
    {\begin{cvitems}
        \item {English: B2}
        \item {Spanish: Native}
        \item {Catalan: Native}
        \item {Driver's License: B}
    \end{cvitems}}
\end{cventries}

\end{document}
